A Kochen-Specker system has at least 22 vectors

### 2014-12-16 paper/main.tex
paper: fix bibtex
paper: sander's text on non-3d systems

% TODO refer to non-3d systems
\subsection{Overview}
In \cite{aow11} Arends, Ouaknine and Wampler (AOW) give a computer aided proof
that a KS system must have at least 18 vectors.  We improve their lower bound
and show that a KS system must have at least 22 vectors.

@@

% attribute mckay for answering questions?
% TODO attribute geng
\clearpage
\bibliography{main}{}
\bibliographystyle{kenta}

>>>>

Before we continue, we would like to make two remarks.
\begin{enumerate}
\item
There is an inconsistency in the literature on how to count the number
of points in a Kochen-Specker system.  One way is to take the minimal
number of points required to be non-010-colorable.
This is how we count in this paper.
Another way is to require that for every pair of orthogonal points
in the system, there is a third point orthogonal to both.
This way of counting is used in~\cite{pavivcic}.
\item
We consider three-dimensional Kochen-Specker systems
for two reasons.
First, every 3-dimensional system can be seen as a higher-dimensional
            system.   The converse if false.
Secondly, the size of the least Kochen-Specker system
            in dimension 4 and higher has already been found.\cite{pavivcic}
            The three-dimensional case is still open.
\end{enumerate}

\subsection{Overview}
In \cite{aow11} Arends, Ouaknine and Wampler (AOW) give a computer aided proof
that a KS system must have at least 18 vectors.  We improve their lower bound
and show that a KS system must have at least 22 vectors.

@@

% attribute mckay for answering questions?
% TODO attribute geng
\clearpage
\bibliography{main}{}
\bibliographystyle{plain}
